Low Infant Birth Weight in Brazil

### 2024-06-29 code/analysis-code/fullanalysis-v1.qmd
Merged GT tables; updated supplement
Revisions

```{r, message=FALSE,  warning=FALSE}
#load needed packages. make sure they are installed.
library(tidyverse) #for data processing/cleaning; includes ggplot2, tidyr, readr, dplyr, stringr, purr, forcats
library(skimr) #for nice visualization of data 
library(here) #to set paths
library(renv) #for package management
library(knitr) #for nice tables
library(kableExtra) #for nice tables
library(gt) #for nice tables
library(gtsummary) #for summary tables
library(ggplot2) #for plotting
library(tidymodels) #for modeling

rm(list=ls()) #clear the environment
```

@@

whereas BW is birthweight in grams, MA is maternal ancestry (Euro-descent, Afro-descent), and $\epsilon$ is the error term.

@@

```{r}
# Model 1: Final model for paper using all data
# Model using recipes and workflows
# Define recipe for model
ML_recipe1 <- recipe(Weightgrams ~ ModifiedColor, data = ML_linear) %>% 
  step_relevel(ModifiedColor, ref_level = "Euro-Descent") %>% # Set reference level for ModifiedColor
  step_dummy(ModifiedColor) # Convert ModifiedColor to dummy variable

@@

# Create a gtsummary table directly from the model
table2 <-
  tbl_regression(ML_fit1, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table2

#Print table
table2

# Save regression output into table
saveRDS(table2, file = here::here("results", "tables", "table2_final.rds"))
```
## Model 1 Performance

@@

# Create a gtsummary table directly from the model
table2_train <-
  tbl_regression(ML_fit1_train, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table2_train

# Save regression output into table
saveRDS(table2_train, file = here::here("results", "tables", "table2_train.rds"))
```
Our results here are not that different from the model run on all the data. Our adjusted R-squared is 0.01, the same as the full model. The RMSE is 488, which is slightly lower than the full model (494), which shows better performance.

@@

# Create a gtsummary table directly from the model
table2_test <-
  tbl_regression(ML_fit1_test, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table2_test

# Save regression output into table
saveRDS(table2_test, file = here::here("results", "tables", "table2_test.rds"))
```

@@

```{r}
# Final model 2 for paper using all data
# Using recipes and workflows
# Define recipe for model
ML_recipe2 <- recipe(Weightgrams ~ ModifiedColor + Age + ModifiedStatus + ModifiedNationality, data = ML_linear) %>% 
  step_relevel(ModifiedColor, ref_level = "Euro-Descent") %>% # Set reference level for ModifiedColor
  step_dummy(all_nominal(), -all_outcomes()) %>% # Convert all nominal variables to dummy variables
  step_normalize(all_numeric_predictors()) # Normalize all numeric predictors

@@

# Create a gtsummary table directly from the model
table3 <- pull_workflow_fit(ML_fit2) %>%
  tbl_regression(exponentiate = FALSE, intercept = TRUE) %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>%
  bold_p()
table3

# Save regression output into table
saveRDS(table3, file = here::here("results", "tables", "table3_final.rds"))
```
Our RMSE is 490 and our r-squared is 0.026.

@@

# Create a gtsummary table directly from the model
table3_train <- pull_workflow_fit(ML_fit2_train) %>%
  tbl_regression(exponentiate = FALSE, intercept = TRUE) %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>%
  bold_p()
table3_train

# Save regression output into table
saveRDS(table3_train, file = here::here("results", "tables", "table3_train.rds"))
```
Our RMSE is 483 and our r-squared is 0.03, a slightly better performance than the full model.

@@

# Create a gtsummary table directly from the model
table3_test <- pull_workflow_fit(ML_fit2_test) %>%
  tbl_regression(exponentiate = FALSE, intercept = TRUE) %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE) %>%
  bold_p()
table3_test

# Save regression output into table
saveRDS(table3_test, file = here::here("results", "tables", "table3_test.rds"))
```
Running the model on our test data, we see no significant results at any alpha level.

@@

```{r}
# Final model 3 for paper using all data
# Using recipes and workflows
# Simple linear model
# Specify recipe
ML_recipe3 <- recipe(Weightgrams ~ Color, data = ML_linear) %>%
  step_relevel(Color, ref_level = "White")

@@

# Create a gtsummary table from model
table4 <- tbl_regression(ML_fit3, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table4

@@

# Create a gtsummary table from model
table4_train <- tbl_regression(ML_fit3_train, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table4_train

# Save regression output into table
saveRDS(table4_train, file = here("results", "tables", "table4_train.rds"))
```

@@

# Create a gtsummary table from model
table4_test <- tbl_regression(ML_fit3_test, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table4_test

# Save regression output into table
saveRDS(table4_test, file = here("results", "tables", "table4_test.rds"))
```

@@

```{r}
# Final model 4 for paper using all data
# Using recipes and workflows
# Complex linear model
# Specify recipe
ML_recipe4 <- recipe(Weightgrams ~ Color + Age + ModifiedStatus + ModifiedNationality, data = ML_linear) %>%
  step_relevel(Color, ref_level = "White") %>% # Set reference level for Color
  step_relevel(ModifiedStatus, ref_level = "Multiparous") %>% # Set reference level for ModifiedStatus
  step_dummy(all_nominal(), -all_outcomes()) %>% # Convert all nominal variables to dummy variables
  step_normalize(all_numeric_predictors()) # Normalize all numeric predictors

@@

# Create a gtsummary table from model
table5 <- tbl_regression(ML_fit4, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table5

# Save regression output into table
saveRDS(table5, file = here("results", "tables", "table5_final.rds"))
```
Our RMSE is 490 and our r-squared is 0.026.

@@

# Create a gtsummary table from model
table5_train <- tbl_regression(ML_fit4_train, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table5_train

# Save regression output into table
saveRDS(table5_train, file = here("results", "tables", "table5_train.rds"))
```
Our RMSE is 483 and our r-squared is 0.033, a slightly better performance than the full model.

@@

# Create a gtsummary table from model
table5_test <- tbl_regression(ML_fit4_test, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table5_test

# Save regression output into table
saveRDS(table5_test, file = here("results", "tables", "table5_test.rds"))
```
Again, most of our results are not significant except the intercept given the small sample size.

>>>>

```{r, message=FALSE,  warning=FALSE}
#load needed packages. make sure they are installed.
#install.packages("glue")
library(tidyverse) #for data processing/cleaning; includes ggplot2, tidyr, readr, dplyr, stringr, purr, forcats
library(skimr) #for nice visualization of data 
library(here) #to set paths
library(renv) #for package management
library(knitr) #for nice tables
library(kableExtra) #for nice tables
library(gt) #for nice tables
library(gtsummary) #for summary tables
library(ggplot2) #for plotting
library(tidymodels) #for modeling
library(glue)
rm(list=ls()) #clear the environment
```

@@

whereas BW is birth weight in grams, MA is maternal ancestry (Euro-descent, Afro-descent), and $\epsilon$ is the error term.

@@

```{r}
# Model 1: Final model for paper using all data
# Model using recipes and workflows
# Define recipe for model
ML_recipe1 <- recipe(Weightgrams ~ ModifiedColor, data = ML_linear) %>% 
  step_relevel(ModifiedColor, ref_level = "Euro-Descent") #%>% # Set reference level for ModifiedColor
  #step_dummy(ModifiedColor) # Convert ModifiedColor to dummy variable. Cannot do this if I am merging tables

@@

# Create a gtsummary table directly from the model
table_model1 <-
  tbl_regression(ML_fit1, exponentiate = FALSE, intercept = TRUE) %>% 
  add_significance_stars(hide_ci = TRUE, hide_p = TRUE) %>%
  add_glance_table(include = c(r.squared, nobs))
table_model1

#Print table
table_model1

# Save regression output into table
saveRDS(table_model1, file = here::here("results", "tables", "table_model1_final.rds"))
```
## Model 1 Performance

@@

# Create a gtsummary table directly from the model
table_model1_train <-
  tbl_regression(ML_fit1_train, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table_model1_train

# Save regression output into table
saveRDS(table_model1_train, file = here::here("results", "tables", "table_model1_train.rds"))
```
Our results here are not that different from the model run on all the data. Our adjusted R-squared is 0.01, the same as the full model. The RMSE is 488, which is slightly lower than the full model (494), which shows better performance.

@@

# Create a gtsummary table directly from the model
table_model1_test <-
  tbl_regression(ML_fit1_test, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table_model1_test

# Save regression output into table
saveRDS(table_model1_test, file = here::here("results", "tables", "table_model1_test.rds"))
```

@@

```{r}
# Final model 2 for paper using all data
# Using recipes and workflows
# Define recipe for model
ML_recipe2 <- recipe(Weightgrams ~ ModifiedColor + Age + ModifiedStatus + ModifiedNationality, data = ML_linear) %>% 
  step_relevel(ModifiedColor, ref_level = "Euro-Descent") #%>% # Set reference level for ModifiedColor
  #step_dummy(ModifiedColor) #%>% # Convert all nominal variables to dummy variables. Cannot do this if I am merging tables in gtsummary
  #step_normalize(all_numeric_predictors()) # Normalize all numeric predictors. Cannot do this if I am merging tables in gtsummary

@@

# Create a gtsummary table directly from the model
table_model2 <- tbl_regression(ML_fit2, exponentiate = FALSE, intercept = TRUE) %>%
  add_significance_stars(hide_ci = TRUE, hide_p = TRUE) %>%
  add_glance_table(include = c(r.squared, nobs))
table_model2

# Save regression output into table
saveRDS(table_model2, file = here::here("results", "tables", "table_model2_final.rds"))
```
Our RMSE is 490 and our r-squared is 0.026.

@@

# Create a gtsummary table directly from the model
table_model2_train <- pull_workflow_fit(ML_fit2_train) %>%
  tbl_regression(exponentiate = FALSE, intercept = TRUE) %>%
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = TRUE, hide_p = TRUE) %>%
  bold_p()
table_model2_train

# Save regression output into table
saveRDS(table_model2_train, file = here::here("results", "tables", "table_model2_train.rds"))
```
Our RMSE is 483 and our r-squared is 0.03, a slightly better performance than the full model.

@@

# Create a gtsummary table directly from the model
table_model2_test <- pull_workflow_fit(ML_fit2_test) %>%
  tbl_regression(exponentiate = FALSE, intercept = TRUE) %>%
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = TRUE, hide_p = TRUE) %>%
  bold_p()
table_model2_test

# Save regression output into table
saveRDS(table_model2_test, file = here::here("results", "tables", "table_model2_test.rds"))
```
Running the model on our test data, we see no significant results at any alpha level.

# Merging Model 1 and 2 into Table

```{r}
# Combine the two tables using tbl_merge
table3 <- tbl_merge(list(table_model1, table_model2), tab_spanner = c("**Model 1**", "**Model 2**")) %>%
  modify_table_body(fun = ~.x %>% arrange(variable))
table3

# Save regression output into table
saveRDS(table3, file = here::here("results", "tables", "table3_final.rds"))
```

@@

```{r}
# Final model 3 for paper using all data
# Using recipes and workflows
# Simple linear model
# Specify recipe
ML_recipe3 <- recipe(Weightgrams ~ Color, data = ML_linear) %>%
  step_relevel(Color, ref_level = "White") #%>% # Set reference level for White
  #step_dummy(all_nominal(), -all_outcomes()) %>% # Convert all nominal variables to dummy variables
  #step_normalize(all_numeric_predictors()) # Normalize all numeric predictors

@@

# Create a gtsummary table from model
table_model3 <- tbl_regression(ML_fit3, exponentiate = FALSE, intercept = TRUE) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = TRUE, hide_p = TRUE) %>%
  add_glance_table(include = c(r.squared, nobs))
table_model3

# Save regression output into table
saveRDS(table_model3, file = here("results", "tables", "table_model3_final.rds"))
```

@@

# Create a gtsummary table from model
table_model3_train <- tbl_regression(ML_fit3_train, exponentiate = FALSE, intercept = TRUE) %>%
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = TRUE, hide_p = TRUE)
table_model3_train

# Save regression output into table
saveRDS(table_model3_train, file = here("results", "tables", "table_model3_train.rds"))
```

@@

# Create a gtsummary table from model
table_model3_test <- tbl_regression(ML_fit3_test, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table_model3_test

# Save regression output into table
saveRDS(table_model3_test, file = here("results", "tables", "table_model3_test.rds"))
```

@@

```{r}
# Final model 4 for paper using all data
# Using recipes and workflows
# Complex linear model
# Specify recipe
ML_recipe4 <- recipe(Weightgrams ~ Color + Age + ModifiedStatus + ModifiedNationality, data = ML_linear) %>%
  step_relevel(Color, ref_level = "White") %>% # Set reference level for Color
  step_relevel(ModifiedStatus, ref_level = "Multiparous") #%>% # Set reference level for ModifiedStatus
  #step_dummy(all_nominal(), -all_outcomes()) %>% # Convert all nominal variables to dummy variables
  #step_normalize(all_numeric_predictors()) # Normalize all numeric predictors

@@

# Create a gtsummary table from model
table_model4 <- tbl_regression(ML_fit4, exponentiate = FALSE, intercept = TRUE) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = TRUE, hide_p = TRUE) %>% # Hide confidence intervals and p-values
    add_glance_table(include = c(r.squared, nobs)) # Add R-squared and number of observations
table_model4

# Save regression output into table
saveRDS(table_model4, file = here("results", "tables", "table_model4_final.rds"))
```
Our RMSE is 490 and our r-squared is 0.026.

@@

# Create a gtsummary table from model
table_model4_train <- tbl_regression(ML_fit4_train, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table_model4_train

# Save regression output into table
saveRDS(table_model4_train, file = here("results", "tables", "table_model4_train.rds"))
```
Our RMSE is 483 and our r-squared is 0.033, a slightly better performance than the full model.

@@

# Create a gtsummary table from model
table_model4_test <- tbl_regression(ML_fit4_test, exponentiate = FALSE, intercept = TRUE) %>%
  bold_p() %>%
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error)) %>%
  add_significance_stars(hide_ci = FALSE, hide_p = FALSE)
table_model4_test

# Save regression output into table
saveRDS(table_model4_test, file = here("results", "tables", "table_model4_test.rds"))
```
Again, most of our results are not significant except the intercept given the small sample size.

## Merge Models 3 and 4
```{r}
# Combine the two tables using tbl_merge
table4 <- tbl_merge(list(table_model3, table_model4), tab_spanner = c("**Model 3**", "**Model 4**")) %>%
  modify_table_body(fun = ~.x %>% arrange(variable))
table4

### 2024-06-29 code/analysis-code/introanalysis-v1.qmd
Merged GT tables; updated supplement
Revisions

# Create a gtsummary table directly from the model
table2 <-
  tbl_regression(ML_fit1, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% # make p-values bold
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))

#Print table
table2

# Save regression output into table
saveRDS(table2, file = here::here("results", "tables", "table2.rds"))
```
Now let's run a second simple bivariate analysis, looking at infant birth weight as a function of maternal age. This time, when plotting weight as a function of maternal age, we can use a scatterplot.

@@

# Create a gtsummary table directly from the model
table_age <-
  tbl_regression(ML_fit_age, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))

#Print table
table_age

# Save regression output into table
saveRDS(table_age, file = here::here("results", "tables", "tableage_final.rds"))
```

@@

# Create a gtsummary table directly from the model
table3 <- tbl_regression(ML_lm3, exponentiate = FALSE, intercept = TRUE) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))
table3

# Save regression output into table
saveRDS(table3, file = here::here("results", "tables", "table3.rds"))
```

@@

# Create a gtsummary table directly from the model
table4 <- tbl_regression(ML_lm4, exponentiate = FALSE, intercept = TRUE) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))
table4

# Save regression output into table
saveRDS(table4, file = here::here("results", "tables", "table4.rds"))

@@

# Specify and fit model using linear_reg() (default engine, OLS) from tidymodels
ML_lm5 <- linear_reg() %>% set_engine("lm") %>% fit(Weightgrams ~ Color + Age + ModifiedStatus + ModifiedNationality, data = ML_linear)

# Summarize model fit with tidiers
ML_lm5_summary <- summary(ML_lm5) # Summary of fit
tidy(ML_lm5, conf.int = TRUE) %>% mutate(p.value = round(p.value, 5)) # Coefficients and confidence intervals with p-values rounded to 5 decimal places
glance(ML_lm5) # Model-level statistics

# Create a gtsummary table directly from the model
table5 <- tbl_regression(ML_lm5, exponentiate = FALSE, intercept = TRUE) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))
table5

# Save regression output into table
saveRDS(table5, file = here::here("results", "tables", "table5.rds"))
```

@@

# Create a gtsummary table directly from the model
table6 <- tbl_regression(log1_fitted, exponentiate = TRUE) # use exponentiate true for ORs
table6

# Save regression output into table
saveRDS(table6, file = here::here("results", "tables", "table6.rds"))

@@

# Create a gtsummary table directly from the model
table7 <- tbl_regression(log2_fitted, exponentiate = TRUE) # use exponentiate true for ORs
table7

# Save regression output into table
saveRDS(table7, file = here::here("results", "tables", "table7.rds"))

@@

# Create a gtsummary table directly from the model
table8 <- tbl_regression(log3_fitted, exponentiate = TRUE) # use exponentiate true for ORs
table8 <- bold_p(table8, t = 0.05)
table8

# Save regression output into table
saveRDS(table8, file = here::here("results", "tables", "table8.rds"))

@@

# Create a gtsummary table directly from the model
table9 <- tbl_regression(log4_fitted, exponentiate = TRUE) # exponentiate true for ORs

#Bold significant p-values
table9 <- bold_p(table9, t = 0.05)
table9

# Save regression output into table
saveRDS(table9, file = here::here("results", "tables", "table9.rds"))

>>>>

# Create a gtsummary table directly from the model
table_fit1 <-
  tbl_regression(ML_fit1, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% # make p-values bold
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))

#Print table
table_fit1

# Save regression output into table
saveRDS(table_fit1, file = here::here("results", "tables", "table_fit1.rds"))
```
Now let's run a second simple bivariate analysis, looking at infant birth weight as a function of maternal age. This time, when plotting weight as a function of maternal age, we can use a scatterplot.

@@

# Create a gtsummary table directly from the model
table_fit2 <-
  tbl_regression(ML_fit_age, exponentiate = FALSE, intercept = TRUE, show_single_row = everything()) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))

#Print table
table_fit2

# Save regression output into table
saveRDS(table_fit2, file = here::here("results", "tables", "table_fit2.rds"))
```

@@

# Create a gtsummary table directly from the model
table_fit3 <- tbl_regression(ML_lm3, exponentiate = FALSE, intercept = TRUE) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))
table_fit3

# Save regression output into table
saveRDS(table_fit3, file = here::here("results", "tables", "table_fit3.rds"))
```

@@

# Create a gtsummary table directly from the model
table_fit4 <- tbl_regression(ML_lm4, exponentiate = FALSE, intercept = TRUE) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))
table_fit4

# Save regression output into table
saveRDS(table_fit4, file = here::here("results", "tables", "table_fit4.rds"))

@@

# Specify and fit model using linear_reg() (default engine, OLS) from tidymodels
ML_lm4 <- linear_reg() %>% set_engine("lm") %>% fit(Weightgrams ~ Color + Age + ModifiedStatus + ModifiedNationality, data = ML_linear)

# Create a gtsummary table directly from the model
table_fit4 <- tbl_regression(ML_lm4, exponentiate = FALSE, intercept = TRUE) %>% 
  bold_p() %>% 
  add_glance_table(include = c(r.squared, adj.r.squared, nobs)) %>%
  modify_column_unhide(columns = c(statistic, std.error))
table_fit4

# Save regression output into table
saveRDS(table_fit4, file = here::here("results", "tables", "table_fit4.rds"))
```

@@

# Create a gtsummary table directly from the model
table_log1 <- tbl_regression(log1_fitted, exponentiate = TRUE) # use exponentiate true for ORs
table_log1

# Save regression output into table
saveRDS(table_log1, file = here::here("results", "tables", "table_log1.rds"))

@@

# Create a gtsummary table directly from the model
table_log2 <- tbl_regression(log2_fitted, exponentiate = TRUE) # use exponentiate true for ORs
table_log2

# Save regression output into table
saveRDS(table_log2, file = here::here("results", "tables", "table_log2.rds"))

@@

# Create a gtsummary table directly from the model
table_log3 <- tbl_regression(log3_fitted, exponentiate = TRUE) # use exponentiate true for ORs
table_log3 <- bold_p(table_log3, t = 0.05)
table_log3

# Save regression output into table
saveRDS(table_log3, file = here::here("results", "tables", "table_log3.rds"))

@@

# Create a gtsummary table directly from the model
table_log4 <- tbl_regression(log4_fitted, exponentiate = TRUE) # exponentiate true for ORs

#Bold significant p-values
table_log4 <- bold_p(table_log4, t = 0.05)
table_log4

# Save regression output into table
saveRDS(table_log4, file = here::here("results", "tables", "table_log4.rds"))

### 2024-06-29 code/eda-code/eda-v1.qmd
Merged GT tables; updated supplement
Revisions

```{r, message=FALSE,  warning=FALSE}
#load needed packages. make sure they are installed.
library(tidyverse) #for data processing/cleaning; includes ggplot2, tidyr, readr, dplyr, stringr, purr, forcats
library(skimr) #for nice visualization of data 
library(here) #to set paths
library(renv) #for package management
library(knitr) #for nice tables
library(kableExtra) #for nice tables
library(gt) #for nice tables
library(gtsummary) #for summary tables
library(ggplot2) #for plotting
library(hrbrthemes) #for nice themes
hrbrthemes::import_roboto_condensed() #import needed fonts for hrbrthemes
rm(list=ls()) #clear the environment
```

@@

```{r}
# Create histogram plot
weight_plot <- ML_summary %>% filter(!is.na(Weightgrams)) %>% #filter out NAs
  ggplot(aes(x = Weightgrams)) +
  geom_histogram(binwidth = 25, fill="#69b3a2") +
  geom_vline(xintercept = c(1500, 4000), linetype = "dashed", color = "red") +  # Add vertical lines that mark normal birthweight
  theme_ipsum() +
  theme(plot.title = element_text(size=15))
plot(weight_plot)

@@

# Combine the two tables
table1.1 <- tbl_merge(
  tbls = list(stratified_color, stratified_sex),
  tab_spanner = c("**Weight by Modified Color**", "**Weight by Sex**"))

# Display the modified table
table1.1

#Save table
saveRDS(table1.1, file = here::here("results", "tables", "table1.1_final.rds"))
```

>>>>

```{r, message=FALSE,  warning=FALSE}
#load needed packages. make sure they are installed.
#install.packages("hrbrthemes")
library(tidyverse) #for data processing/cleaning; includes ggplot2, tidyr, readr, dplyr, stringr, purr, forcats
library(skimr) #for nice visualization of data 
library(here) #to set paths
library(renv) #for package management
library(knitr) #for nice tables
library(kableExtra) #for nice tables
library(gt) #for nice tables
library(gtsummary) #for summary tables
library(ggplot2) #for plotting
library(hrbrthemes) #for nice themes
hrbrthemes::import_roboto_condensed() #import needed fonts for hrbrthemes
rm(list=ls()) #clear the environment
```

@@

```{r}
# Create histogram plot
weight_plot <- ML_summary %>% filter(!is.na(Weightgrams)) %>% #filter out NAs
  ggplot(aes(x = Weightgrams)) +
  geom_histogram(binwidth = 25, fill="#69b3a2") +
  geom_vline(xintercept = c(2500, 4000), linetype = "dashed", color = "red") +  # Add vertical lines that mark normal birthweight
  theme_ipsum() +
  theme(plot.title = element_text(size=15))
plot(weight_plot)

@@

# Combine the two tables
table2 <- tbl_merge(
  tbls = list(stratified_color, stratified_sex),
  tab_spanner = c("**Weight by Modified Color**", "**Weight by Sex**"))

# Display the modified table
table2

#Save table
saveRDS(table2, file = here::here("results", "tables", "table2_final.rds"))
```

### 2024-06-29 products/manuscript/Manuscript_Draft.qmd
Merged GT tables; updated supplement
Revisions

```{r, echo=FALSE, message=FALSE}
#Loading packages
#install.packages("flextable")
#install.packages("gdtools")
library(tidyverse) #for data processing/cleaning
library(skimr) #for nice visualization of data 
library(here) #to set paths
library(renv) #for package management
library(gtsummary) #for summary tables
library(flextable) #for nice tables
```

>>>>

```{r, echo=FALSE, message=FALSE}
#Loading packages
#install.packages("flextable")
#install.packages("gdtools")
#install.packages("tidyverse")
library(tidyverse) #for data processing/cleaning
library(skimr) #for nice visualization of data 
library(here) #to set paths
library(renv) #for package management
library(gtsummary) #for summary tables
library(flextable) #for nice tables
```
